Data_Analysis_exp7

### 2017-12-29 Traditional_Analysis/Analysis_exp7_2.rmd
re-check the code

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

df.corr.bias_acc <- merge(df.L1.V.acc_w[,c(1,10:13)],df.T1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
df.corr.bias_acc <- df.corr.bias_acc[,2:13]
acc_bias.corr <- corr.test(df.corr.bias_acc,use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE)
postscript("corr_acc_bias_p_05.eps", width = 2048, height = 1024)
#:main = "corr coefficient (matching-categorization) - ACC_bias"
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
```

@@

The correlation between the self-bias and moral bias of RT of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_RT-bias,echo=FALSE,warning=FALSE,message=FALSE }
# merge the data by subj ID
df.corr.bias_rt <- merge(df.L1.V.RT.subj_w[,c(1,10:13)],df.T1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
df.corr.bias_rt <- df.corr.bias_rt[,2:13]
rt_bias.corr <- corr.test(df.corr.bias_rt)

>>>>

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

df.corr.bias_acc <- merge(df.L1.V.acc_w[,c(1,10:13)],df.T1.V.acc.subj_w[,c(1,10:17)],by = 'Subject')
write.csv(df.corr.bias_acc,"df.corr.bias_acc.csv",row.names = F)
df.corr.bias_acc <- df.corr.bias_acc[,2:13]
acc_bias.corr <- corr.test(df.corr.bias_acc,use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE)
postscript("corr_acc_bias_p_05.eps", width = 2048, height = 1024)
#:main = "corr coefficient (matching-categorization) - ACC_bias"
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
dev.off()
corrplot.mixed(acc_bias.corr[[1]],p.mat = acc_bias.corr[[4]],sig.level = 0.05,insig = "blank")
```

@@

The correlation between the self-bias and moral bias of RT of match trials in match task and ACC of categorization task
```{r correlattion between learning and testing_RT-bias,echo=FALSE,warning=FALSE,message=FALSE }
# merge the data by subj ID
df.corr.bias_rt <- merge(df.L1.V.RT.subj_w[,c(1,10:13)],df.T1.V.RT.subj_w[,c(1,10:17)],by = 'Subject')
write.csv(df.corr.bias_rt,"df.corr.bias_rt.csv",row.names = F)
df.corr.bias_rt <- df.corr.bias_rt[,2:13]
rt_bias.corr <- corr.test(df.corr.bias_rt)
